\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in R

### 2014-01-22 papers/jss/article.Rnw
copy/paste typo
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@814 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\begin{verbatim}
  protoc histogram.proto --python_out=.
\end{verbatim}
This generates Python module called \texttt{histogram\_pb2.py}, containing both the 
descriptor information as well as methods to read and manipulate the R object 
message.

>>>>

\begin{verbatim}
  protoc histogram.proto --python_out=.
\end{verbatim}
This generates Python module called \texttt{histogram\_pb2.py}, containing both the 
descriptor information as well as methods to read and manipulate the histogram 
message data.
